Paper Figs

### 2023-09-27 graphs_newt_snakes/Paper_figs.Rmd
made some fig improvements

  plot <-  ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, "th generation to ", max_gen, "th generation"))+
  xlab(x_label) + ylab(y_label)+
  geom_boxplot(aes(x=factor(sim, level=c('Sims', "F","G","H","J","K","L","N","O","P")), y=as.numeric(mean_newt_pheno_By_mean_snake_pheno), fill=factor(cor_score)))+
  theme(plot.title = element_text(size=5)) +
  #xlim(-1.1, 1.1)+
    geom_hline(yintercept=real_snewt_cor, linetype="dashed")+
  facet_wrap(~exp, ncol=1)+
  scale_fill_manual(values =c("darkolivegreen3", "cadetblue2"), labels=c('Low Mutational Variance', 'Coevolution'))+
    labs(fill = " ")+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 18),
                      title =element_text(size=18, face='bold'), legend.text=element_text(size=16), strip.text.x = element_text(size = 20))

@@

file1 = GA1_cor
file2 = cost_grade_cor
file3 = interrate_grade
file4 = cost_grade_no_interact_cor
file5 = snake_change_cor
file6 = newt_change_cor
title = "Spatial Phenotype Correlation"
subt = " "
exp_labeles=c("Flat Map", "Cost Gradent Map", "Interaction Gradent Map")
x_label = "Simulations"
y_label = "Spatial Correlation"
min_gen = 40000
max_gen = 50000

@@

  plot <-  ggplot(file) +
  ggtitle(title)+
  xlab(x_label) + ylab(y_label)+
  geom_boxplot(aes(x=factor(sim), y=as.numeric(newt_snake_pheno_avg), fill=factor(exp)))+
  theme(plot.title = element_text(size=5)) +
  #xlim(-1.1, 1.1)+
  scale_fill_manual(values =c("darkolivegreen1", "azure2", "darkorange3"), labels=c("No Interaction", "No Heritability", "Standard Simulation"))+
    labs(fill = " ")+
  theme_bw() +  theme(title =element_text(size=18, face='bold'), legend.text=element_text(size=16), strip.text.x = element_text(size = 20)) #axis.text.x = element_text(angle = 45, hjust=1, size = 18),

@@

title = "Total Phenotype Change"
subt = "Three Experiments"
x_label = "Simulation"
y_label = "Change in Phenotype"

@@

```{r, plotting all of the changes}
title = "Coevolution Slope (Phenotype Change/ Time)"
subt = "Simulation F, J, G, K"
GA_stage_long <- tidyr::pivot_longer(GA_stage, c(newt_coevo_slope, snake_coevo_slope))
y_label="Coevolution Speed"
x_label="Genetic Architectures (red=newt, blue=snake)"

>>>>

  plot <-  ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, "th generation to ", max_gen, "th generation"))+
  xlab(x_label) + ylab(y_label)+
  geom_boxplot(aes(x=factor(sim, level=c('Sims', "F","G","H","J","K","L","N","O","P")), y=as.numeric(mean_newt_pheno_By_mean_snake_pheno), fill=factor(cor_score)))+
  theme(plot.title = element_text(size=5)) +
    scale_x_discrete(breaks=c('Sims',"F","G","H", "J", "K", "L", "N", "O", "P"), labels=c("1a's", "2a/2a", "2a/3a", "2a/4a", "3a/2a", "3a/3a", "3a/4a", "4a/2a", "4a/3a", "4a/4a")) + 
  #  level=c("1a's", "2a/2a", "2a/3a", "2a/4a", "3a/2a", "3a/3a", "3a/4a", "4a/2a", "4a/3a", "4a/4a")+
  #xlim(-1.1, 1.1)+
    geom_hline(yintercept=real_snewt_cor, linetype="dashed")+
  facet_wrap(~exp, ncol=1)+
  scale_fill_manual(values =c("darkolivegreen3", "cadetblue2"), labels=c('Low Mutational Variance', 'Coevolution'))+
    labs(fill = " ")+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 18),
                      title =element_text(size=18, face='bold'), legend.text=element_text(size=16), strip.text.x = element_text(size = 20))

@@

file1 = GA1_cor
file2 = cost_grade_cor
file3 = interrate_grade
file4 = cost_grade_no_interact_cor
file5 = snake_change_cor
file6 = newt_change_cor
title = "Spatial Phenotype Correlation"
subt = " "
exp_labeles=c("Flat Map", "Cost Gradent Map", "Interaction Gradent Map")
x_label = "Newt/Snake Genetic Architecture"
y_label = "Spatial Correlation"
min_gen = 40000
max_gen = 50000

@@

  plot <-  ggplot(file) +
  ggtitle(title)+
  xlab(x_label) + ylab(y_label)+
  geom_boxplot(aes(x=factor(sim), y=as.numeric(newt_snake_pheno_avg), fill=factor(exp)))+
  theme(plot.title = element_text(size=5)) +
  #xlim(-1.1, 1.1)+
  scale_fill_manual(values =c("darkolivegreen1", "azure2", "darkorange3"), labels=c("No Interaction", "No Heritability", "Standard Simulation"))+
    scale_x_discrete(breaks=c("F","G","H", "J", "K", "L", "N", "O", "P"), labels=c("2a/2a", "2a/3a", "2a/4a", "3a/2a", "3a/3a", "3a/4a", "4a/2a", "4a/3a", "4a/4a")) + # label newt/snake
    labs(fill = " ")+
  theme_bw() +  theme(title =element_text(size=18, face='bold'), legend.text=element_text(size=16), strip.text.x = element_text(size = 20)) #axis.text.x = element_text(angle = 45, hjust=1, size = 18),

@@

title = "Total Phenotype Change"
subt = "Three Experiments"
x_label = "Simulation Genetic Architecture"
y_label = "Change in Phenotype"

@@

```{r, plotting all of the changes}
title = "Coevolution Slope"
subt = "Simulation F, J, G, K"
GA_stage_long <- tidyr::pivot_longer(GA_stage, c(newt_coevo_slope, snake_coevo_slope))
y_label="Coevolution Speed (Phenotype Change/ Time)"
x_label="Genetic Architectures (red=newt, blue=snake)"
